%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Sr. Staff Software Engineer} % Job title
    {Kyruus Health} % Organization
    {Portland, Oregon (Remote)} % Location
    {Feb. 2025 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Drove strategic technical transformation by leading the Biome design system team and influencing the Frontend Platform initiative, delivering a proof of concept that shaped the company's frontend architecture.}
        \item {Drove product excellence by leading a major revamp of the marketable location page—setting direction, aligning stakeholders, and ensuring high-impact delivery aligned with business goals.}
        \item {Built a strong mentorship culture by onboarding engineers, pairing frequently, and helping teammates grow technical confidence and clarity through thoughtful communication.}
        \item {Championed collaboration and transparency as a liaison between design system and frontend teams, fostering alignment and accelerating progress through clear communication and relationship-building.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Staff Software Engineer} % Job title
    {Kyruus Health} % Organization
    {Portland, Oregon (Remote)} % Location
    {Jul. 2022 - Feb. 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led a cross-functional initiative to optimize Provider Profile and Search experiences, resulting in a 13\% increase in appointment bookings. Focused on improving UX, performance, and accessibility to enhance patient engagement and drive conversion. (Tech: AI, Node.js, TypeScript, React)}
        \item {Mentored peers through code reviews, pair programming, and inclusive collaboration practices, fostering a team culture of shared learning, high code quality, and mutual respect.}
        \item {Expanded systems and observability expertise (DataDog, DevOps pipelines) while deepening architectural knowledge to support long-term technical strategy and cross-team initiatives.}
        \item {Championed incremental release strategies, accelerating delivery cycles and increasing customer value through smaller, more reliable product rollouts.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lead Software Engineer} % Job title
    {Penta Technologies, Inc.} % Organization
    {Portland, Oregon (Remote)} % Location
    {Dec. 2021 - Jul. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built and maintained a complex union ERP frontend designed to help users make more intelligent and accurate accounting decisions. (Tech: NodeJS, TypeScript, React)}
        \item {Peer reviewed code for best practices and design guidelines. (Tech: TypeScript, React)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Principal Software Engineer} % Job title
    {Webtrends} % Organization
    {Portland, Oregon (Remote)} % Location
    {Jul. 2019 - Dec. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Architected and developed an SSO implementation providing secure access to Webtrends products. (Tech: C\#, NodeJS, TypeScript, React, Web API 2, OpenID, OAuth 2.0)}
        \item {Created a Webtrends tag deployment app for SharePoint providing customers with a simple and seamless on boarding process for large SharePoint tenancies. (Tech: NodeJS, React, TypeScript, Sharepoint, REST)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Sr. Software Engineer} % Job title
    {Oracle} % Organization
    {Portland, Oregon} % Location
    {Jul. 2018 - Jul. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working with other engineers on a diverse team, maintained and enhanced complex web analytics visualizations. (Tech: NodeJS, TypeScript, React)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Sr. Software Engineer} % Job title
    {Webtrends} % Organization
    {Portland, Oregon} % Location
    {Mar. 2017 - Jul. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Collaborating with designers and business stake holders, developed a suite of customer account management applications providing authentication, session management, and account and user permissions. (Tech: NodeJS, React, HTML5, CSS3, SAML, REST)}
        \item {Working with operations teams, developed internal tools engineered to automate and simplify complex development processes. (Tech: Ruby, Chef, Rundeck, Jenkins)}
        \item {Performed code reviews to ensure code quality standards were met and best practices were followed. (Tech: JavaScript, .NET, C\#, JAVA, Ruby)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Sr. Software Developer} % Job title
    {Webtrends} % Organization
    {Portland, Oregon} % Location
    {Dec. 2013 - Mar. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {In effort to automate the full customer SaaS life cycle, from account provisioning to billing, created middleware to integrate internal and external systems. (Tech: .NET, C\#, PHP, JS, SOAP, REST, APEX, Visualforce, MSSQL)}
        \item {To promote customer adoption and long-term customer success, developed a customer portal providing several features such as forums, case management, and documentation. (Tech: APEX, Visualforce, JS, HTML, APIs)}
        \item {To ensure code quality, efficiency, and reduce technical debt, performed design and code reviews of customer facing products. (Tech: .NET, C\#, C++, JS, PY, JAVA, Ruby)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Web Systems Engineer} % Job title
    {Webtrends} % Organization
    {Portland, Oregon} % Location
    {Apr. 2012 - Dec. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Collaborating with front-end designers and developers, developed a multi-tier CMS for public facing documentation and marketing materials. (Tech: PHP, JS, APIs)}
        \item {To reduce manual processes and provide long-term auditability, developed a multi-tier change management application. (Tech: .Net, ASP.NET MVC, EF, C\#, JS, REST)}
        \item {In conjunction with other engineers, developed and maintained console applications, web applications, web services, and APIs. This effort supported many departments ranging from finance to engineering. (Tech: .NET, ASP.NET MVC, EF, CodeIgniter, WordPress, PHP, C\#, JS, SOAP, REST)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {System Administrator} % Job title
    {Concise Solutions, Inc.} % Organization
    {Portland, Oregon (Remote)} % Location
    {Aug. 2007 - Apr. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {In efforts to provide customers with a HIPAA compliant healthcare reimbursement application, assisted in developing an expense reimbursement application. (Tech: PHP, JS, MySQL)}
        \item {To migrate from an outdated and unsupported series of disjointed systems, created an infrastructure plan to serve a remote workforce and provide a greater level of security. (Tech: Windows, Linux)}
        \item {Working in conjunction with internal users, built and administered internal production servers and networking infrastructure. (Tech: Windows, Linux)}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
